---
output: 
  pdf_document:
    includes:
      in_header: header.tex
params:
  po.id: po.id
  po.info.general: po.info.general
  po.info.garments: po.info.garments
  po.info.garments.flow: po.info.garments.flow
  po.info.materials: po.info.materials
sansfont: Calibri light
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F,
                      warning = F)
```

***

\begin{vwcol}[widths={0.3,0.7},
 sep=.8cm, justify=flush,rule=0pt,indent=1em] 
   \null \vfill
  \includegraphics[width=.2\textwidth]{./Acceso/LOGO.jpg}
  \vfill \null
  
\newpage
  
  \null \vfill
  \section{\fontsize{50}{15}\selectfont Full Body}
  \vfill \null
 \end{vwcol}
 
``` {r echo = FALSE}
subtitle <- paste0('Orden de producción \\#',
                   params$po.id)
```

 
\section{\fontsize{25}{15}\selectfont \hfil `r subtitle`\hfil}
\bigskip
\bigskip

\section{\fontsize{15}{15}\selectfont \hfil Información General\hfil}
\medskip
 
``` {r echo = FALSE, results = 'asis'}

library(knitr)
library(xtable)


t1 <- knitr::kable(params$po.info.general,
               format = 'latex',
               booktabs = T,
               col.names = c('Información', ''),
               linesep = ""
               #align = 'l',
               #padding = 20
               )

b <- as.data.frame(t(params$po.info.garments))
b$names <- c('Prenda',
             'Cantidad original',
             'Corte',
             'Recibido')
b <- b[, c('names', 'V1')]
                   
t2 <- knitr::kable(b,
             format = 'latex', 
             col.names = c('Prendas recibidas', ''),
             row.names = F,
             booktabs = T,
             linesep = "")

t3 <- knitr::kable(params$po.info.materials,
               format = 'latex',
               booktabs = T, 
               col.names = c('Nombre', 
                             'Cantidad acordada',
                             'Cantidad entregada',
                             'Costo'),
               linesep = ""
               #align = 'l',
               #padding = 20
               )

t4 <- knitr::kable(params$po.info.garments.flow,
               format = 'latex',
               booktabs = T, 
               col.names = c('ID sistema',
                             'ID alternativo',
                             'Fecha recibo',
                             'Prenda',
                             'Cantidad'),
               linesep = ""
               #align = 'l',
               #padding = 20
               )


cat(c("\\begin{table}[!htb]
    \\begin{minipage}[t]{.5\\linewidth}
      \\vspace{0pt}
      \\centering",
        t1,
    "\\end{minipage}%
    \\begin{minipage}[t]{.5\\linewidth}
      \\vspace{0pt}
      \\centering",
        t2,
    "\\end{minipage} 
\\end{table}"
))

# cat(c('\\centering', t3))

``` 
\section{\fontsize{15}{15}\selectfont \hfil Materiales\hfil}
\medskip

\begin{center}
`r t3`
\end{center}
 
 \section{\fontsize{15}{15}\selectfont \hfil Recibos prendas\hfil}
\medskip

\begin{center}
`r t4`
\end{center}

\bigskip
\bigskip

***